The Sound of Teaching Music: Expert Pianists' Performance Modulations for Novices

### 2021-01-12 paper/manuscript.Rmd
delete irrelevant folders
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

documentclass     : "apa6"
classoption       : "man"
output: papaja::apa6_docx
---
```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"); require("papaja")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("magick")) {install.packages("magick"); require("magick")}

>>>>

documentclass     : "apa6"
classoption       : "man"
output: papaja::apa6_docx

---
```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"); require("papaja")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("magick")) {install.packages("magick"); require("magick")}
